\newpage
\section*{Motivation} \label{motivation}
In recent years, we have witnessed a proliferation of mobile devices with global positioning 
(GPS) functionality and internet connectivity. This has led to a rapid emergence and a notable 
progress in the development of Location-based Service (LBS). The typical examples of LBS
include automotive traffic monitoring, network resource allocation, location-based 
targeted advertisements and social networking. A large amount of user data is collected by the 
service providers and is used to train user specific learning models, in order to predict user 
mobility and behavioural patterns. Although LBS offer valuable services, revealing personal location 
data to potentially untrustworthy service providers raises several privacy concerns.\newline

The heart of the thesis will be augmenting the current mobility prediction learning frameworks in order
to incorporate privacy awareness as a key paradigm. Meanwhile, researchers today use cryptographic
techniques and Location Privacy Preserving Mechanisms (LPPM) for privacy preservation, which are 
computationally complex and do not facilitate collaborative learning. We will also explore 
distributed means of computing user independent learning models in realtime. According to recent 
surveys, 55\% of LBS users have shown concern towards loss of their location privacy and about 50\% of 
U.S. residents who have a profile on social networking sites are concerned about their privacy~\cite{4511454}. 
It is clear that, the success of LBS depends on their ability to maintain location privacy in the near future,
where the users preserve the privacy of their location data while still benefitting from the LBS, thus 
maintaining the utility-privacy space.\newline

Since the major component of this research lies in a privacy-aware mobility prediction framework, we
limit the literature survey to these two critical topics, mobility prediction and privacy aware- 
computation. Firstly, it is important to understand to what extent, human mobility is predictable. 
To this end, we review a classical paper which provides insights into human mobility and
prediction limits. Once the location data is collected, it is necessary to understand how to extract 
the mobility patterns of individuals. We perform a thorough survey in this area and review two
papers that highlight how to discover mobility patterns and user profiles from raw GPS logs. Next, 
we review literature related to existing privacy preserving mobility prediction models. In this
area, we present an article, that depicts a technique to preserve location privacy maintaining the 
quality of services offered by the LBS and highlight several limitations of the method. 
Finally, we survey machine learning techniques, which can be utilised to construct user mobility 
models. In this area, we review a paper, that presents a novel architecture of privacy-preserving 
distributed learning approach.  



